Enhancing diagnostic of stochastic mortality models leveraging contrast trees. An application on Italian data

### 2022-11-08 Manuscript Contrast Trees_R1.tex
predictor

We consider the Italian mortality data available in the Human Mortality Database (HMD) over the period 1950-2018. We refer to the male population aged \color{blue}0-90, analyzing the age groups 0-29, 30-60, and 61-90 separately to provide further evidence of the differences in mortality that characterizes the younger ages, the adult ages, and the older ages. 
We split the data set into training set (fitting period) and test set (out-of-sample forecast period) according to the common rule 70\%-30\%. We will calculate the in-sample errors using data of the training set, and the out-of-sample errors using data of the test set (not used to build the training predictor).
\color{black}
The dataset partition is obtained by using the dissimilarity-based compound selection proposed in \cite{Willett1999}.

>>>>

We consider the Italian mortality data available in the Human Mortality Database (HMD) over the period 1950-2018. We refer to the male population aged \color{blue}0-90, analyzing the age groups 0-29, 30-60, and 61-90 separately to provide further evidence of the differences in mortality that characterizes the younger ages, the adult ages, and the older ages. 
We split the data set into training set and test set according to the common rule 70\%-30\%. The training set is used to obtain the parameters' estimate of each model. In the test set, we apply the parameters' estimate to evaluate the out-of-sample performance. We will calculate the out-of-sample errors using data of the test set.
\color{black}
The dataset partition is obtained by using the dissimilarity-based compound selection proposed in \cite{Willett1999}.
